From Freebase to Wikidata: The Great Migration

### 2015-10-05 paper.tex
Typo detail
Some abstract and author tuning.

\numberofauthors{3}
\author{
Thomas Pellissier Tanon, Denny Vrandečić\\
   \affaddr{Google, San Francisco}\\
   \email{\{thomaspt, vrandecic\}@google.com}
\alignauthor
Sebastian Schaffert\\
   \affaddr{Google, Zurich}\\
   \email{schaffert@google.com}
\alignauthor
Thomas Steiner\\
   \affaddr{Google, Hamburg}\\
   \email{tsteiner@google.com}
}

@@

\begin{abstract}
Freebase was a~collaborative knowledge base created in 2007 and acquired by Google in 2010.
Wikidata is a~collaborative knowledge base created by the Wikimedia movement in 2012.
Due to the success of Wikidata, Google decided to shut down Freebase and
help with the transfer of its content to Wikidata.
In this paper, we describe some of the ongoing transfer effort and challenges,
and provide an analysis of the transfer so far.
\end{abstract}

@@

The quality of the data in Freebase was challenged by the Wikidata community.
For example, a~small city in France had an ISO country code%
\footnote{See \url{http://www.freebase.com/m/03cc0d0}}.
Another example, Boston (the city in Massachusetts) has the type \textit{/people/person}.
A fully automatic upload of all the content from Freebase into Wikidata
did not seem advisable as the expectations of the community regarding
the quality of the content automatically added to Wikidata are high (and rightly so).
Also, whereas an upload of all the data might have lead to accelerated growth
in the short term, such a~fast upload might also endanger the sense of ownership
the Wikidata community has for its data.
Instead we decided to rely on human curation and created Primary Sources,
a simple tool which displays statements to the user that may be added to the currently shown item.
The user can, with only one click, reject the statement or approve it and save it to Wikidata.
It is currently available as a~gadget, an opt-in option in Wikidata.
This tool has no dependencies on Freebase and may be easily reused by other projects
which may want to import data into Wikidata.
For that we have implemented an upload API and a~feature that allows users
to display only statements from a~given dataset.
In fact, during the project one other researcher approached us in order to upload
a dataset extracted from natural language text.
A statistics dashboard has also been created in order to monitor the curation work
\url{https://tools.wmflabs.org/wikidata-primary-sources/status.html}
and the source code of the tool is available on GitHub:
\url{https://github.com/google/primarysources}.

>>>>

\numberofauthors{3}
\author{
Thomas Pellissier Tanon,\titlenote{The author was an intern at Google when the majority of the work was done.}\ Denny Vrandečić\\
   \affaddr{Google, San Francisco, United States of America}\\   
   \email{\{thomaspt, vrandecic\}@google.com}
\alignauthor
Sebastian Schaffert\\
   \affaddr{Google, Zurich, Switzerland}\\   
   \email{schaffert@google.com}
\alignauthor
Thomas Steiner\\
   \affaddr{Google, Hamburg, Germany}\\   
   \email{tsteiner@google.com}
}

@@

\begin{abstract}
Collaborative knowledge bases that make their data available in machine-readable form
as structured data are central to many companies' data strategies.
One example of such collaborative knowledge bases is Freebase (\url{www.freebase.com}),
created with proprietary technologies in 2007 by a~company called Metaweb,
which was then acquired by Google in 2010.
Another example is Wikidata (\url{www.wikidata.org}),
a~collaborative knowledge base developed in the open since 2012 by Wikimedia Deutschland
and operated by the Wikimedia Foundation.
Due to the success of Wikidata, Google decided to shut down Freebase and
help with the transfer of its content to Wikidata through a~crowdsourcing approach.
In this paper, we describe the ongoing transfer efforts and challenges,
and provide an analysis of the process so far.
\end{abstract}

@@

The quality of the data in Freebase was challenged by the Wikidata community.
For example, a~small city in France had an ISO country code%
\footnote{See \url{http://www.freebase.com/m/03cc0d0}}.
Another example, Boston (the city in Massachusetts) has the type \texttt{/people/person}.
A fully automatic upload of all the content from Freebase into Wikidata
did not seem advisable as the expectations of the community regarding
the quality of the content automatically added to Wikidata are high (and rightly so).
Also, whereas an upload of all the data might have lead to accelerated growth
in the short term, such a~fast upload might also endanger the sense of ownership
the Wikidata community has for its data.
Instead we decided to rely on human curation and created Primary Sources,
a simple tool which displays statements to the user that may be added to the currently shown item.
The user can, with only one click, reject the statement or approve it and save it to Wikidata.
It is currently available as a~gadget, an opt-in option in Wikidata.
This tool has no dependencies on Freebase and may be easily reused by other projects
which may want to import data into Wikidata.
For that we have implemented an upload API and a~feature that allows users
to display only statements from a~given dataset.
In fact, during the project one other researcher approached us in order to upload
a dataset extracted from natural language text.
A statistics dashboard has also been created in order to monitor the curation work
\url{https://tools.wmflabs.org/wikidata-primary-sources/status.html}
and the source code of the tool is available on GitHub:
\url{https://github.com/google/primarysources}.
